%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Simple LaTeX CV Template %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Modernized (monochrome, ATS/OCR-safe) typography & spacing pass, dmr 2026

\documentclass[10.5pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Cleaner, more legible text font (still a plain sans-safe serif face,
% no italics/oblique issues for OCR). Comment out to fall back to
% Computer Modern.
\usepackage{fontenc}[T1]
\usepackage{newpxtext}     % Palatino-like text font, more polished than CM
\usepackage[scaled=0.92]{helvet} % used only for section-label small caps feel

\usepackage{calc}
\reversemarginpar

\usepackage[paper=letterpaper,
            marginparwidth=1.2in,
            marginparsep=.06in,
            margin=.7in,
            includemp]{geometry}

\setlength{\parindent}{0in}

\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{microtype}   % subtle kerning/tracking polish, big visual upgrade for free

\usepackage{etaremune}

\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newlist{bibsection}{itemize}{3}
\setlist[bibsection]{label=,leftmargin=\bibhang,%
        itemindent=-\bibhang,
        itemsep=\bibsep,parsep=\z@,partopsep=0pt,
        topsep=0pt}
\newlist{bibenum}{enumerate}{3}
\setlist[bibenum]{label=[\arabic*],resume,leftmargin={\bibhang+\widthof{[999]}},%
        itemindent=-\bibhang,
        itemsep=\bibsep,parsep=\z@,partopsep=0pt,
        topsep=0pt}
\let\oldendbibenum\endbibenum
\def\endbibenum{\oldendbibenum\vspace{-.6\baselineskip}}
\let\oldendbibsection\endbibsection
\def\endbibsection{\oldendbibsection\vspace{-.6\baselineskip}}
\makeatother

\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}

\rhead{\footnotesize\sffamily Rasmussen \textbardbl\ p.~\arabic{page} of \protect\pageref*{LastPage}}

\makeatletter
\let\oldps@plain\ps@plain
\renewcommand{\ps@plain}{\oldps@plain%
\renewcommand{\@evenfoot}{\hspace*{-\footpageshift}\hfil %
    \footnotesize\sffamily p.~\arabic{page} of \protect\pageref*{LastPage}%
    \hfil}%
\renewcommand{\@oddfoot}{\@evenfoot}}
\makeatother

\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{breaklinks,colorlinks,
            linkcolor=black,urlcolor=black,
            anchorcolor=black,citecolor=black,
            }

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Heading: name set in a crisp sans face for contrast against the serif
% body text, with a slightly heavier rule.
\newcommand{\makeheading}[2][]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
             {\Large\sffamily\bfseries\let\FE\fontencoding #2 \hfill\normalfont #1}\\[0.1\baselineskip]%
                 \rule{\columnwidth}{1.1pt}%
         \end{minipage}}

% Section headings: sans-serif small caps in the left margin, letterspaced
% slightly for a more "designed" feel while staying OCR-friendly.
\renewcommand{\section}[1]{\pagebreak[3]%
    \vspace{1.4\baselineskip}%
    \phantomsection\addcontentsline{toc}{section}{#1}%
    \noindent\llap{\sffamily\bfseries\smash{\parbox[t]{\marginparwidth}{\hyphenpenalty=10000\raggedright\MakeUppercase{#1}}}}%
    \vspace{-\baselineskip}\par}

%%% LISTS

\newcommand*\fixendlist[1]{%
    \expandafter\let\csname preFixEndListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\csname preFixEndListend#1\endcsname\vspace{-0.6\baselineskip}}}

\let\originalItem\item
\newcommand*\fixouterlist[1]{%
    \expandafter\let\csname preFixOuterList#1\expandafter\endcsname\csname #1\endcsname
    \expandafter\def\csname #1\endcsname{\csname preFixOuterList#1\endcsname\let\oldItem\item\def\item{\pagebreak[2]\oldItem}}
    \expandafter\let\csname preFixOuterListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\let\item\oldItem\csname preFixOuterListend#1\endcsname}}
\newcommand*\fixinnerlist[1]{%
    \expandafter\let\csname preFixInnerList#1\expandafter\endcsname\csname #1\endcsname
    \expandafter\def\csname #1\endcsname{\let\oldItem\item\let\item\originalItem\csname preFixInnerList#1\endcsname}
    \expandafter\let\csname preFixInnerListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\csname preFixInnerListend#1\endcsname\let\item\oldItem}}

\newlist{outerlist}{itemize}{3}
    \setlist[outerlist]{label=\enskip\textbullet,leftmargin=*}
    \fixendlist{outerlist}
    \fixouterlist{outerlist}

\newlist{lonelist}{itemize}{3}
    \setlist[lonelist]{label=\enskip\textbullet,leftmargin=*,partopsep=0pt,topsep=0pt}
    \fixendlist{lonelist}
    \fixouterlist{lonelist}

\newlist{innerlist}{itemize}{3}
    \setlist[innerlist]{label=\enskip\textbullet,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt}
    \fixinnerlist{innerlist}

\newlist{loneinnerlist}{itemize}{3}
    \setlist[loneinnerlist]{label=\enskip\textbullet,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt}
    \fixendlist{loneinnerlist}
    \fixinnerlist{loneinnerlist}

\newcommand{\blankline}{\quad\pagebreak[3]}
\newcommand{\halfblankline}{\quad\vspace{-0.5\baselineskip}\pagebreak[3]}

\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}

\providecommand*\url[1]{\href{#1}{#1}}
\renewcommand*\url[1]{\href{#1}{\texttt{\small#1}}}

\providecommand*\email[1]{\href{mailto:#1}{#1}}

\hyphenation{bio-mim-ic-ry bio-in-spi-ra-tion re-us-a-ble pro-vid-er}

% Small helper for the year labels used throughout (experience, awards,
% presentations, etc.) so they read as a clean sans-serif column instead
% of italic-slanted numerals.
\newcommand{\yr}[1]{\sffamily\bfseries #1\normalfont}

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makeheading{D.~J.~Rasmussen, Ph.D.}

\newlength{\rcollength}\setlength{\rcollength}{1.85in}%
\newlength{\spacewidth}\setlength{\spacewidth}{20pt}
\newcommand\spacechar{$|$}%

\section{Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.5in}p{4in}}
Email: \email{dj.rasmussen@princeton.edu}\\
WWW: \href{https://www.djrasmussen.co/}{www.djrasmussen.co} \\
 \href{http://scholar.google.com/citations?user=yocPWzYAAAAJ&hl=en}{Google Scholar} \\
 \textit{ORCID:} \href{https://orcid.org/0000-0003-4668-5749}{0000-0003-4668-5749} \\
\end{tabular}

\section{Research Interests}
sea-level rise and coastal floods (physical science), coastal flood defense (social aspects), decision-making under uncertainty, natural hazard risk management, policy process for public works, environmental policy, climate change (physical science)

\section{Recent Professional Experience}
\begin{itemize} [labelindent=1.5em,labelsep=1.0cm,leftmargin=2.75cm]
\item[\yr{2022--now}]  Climate Analytics Practitioner
\item[\yr{2021--2022}]  Postdoctoral Research Associate, School of Public and International Affairs, Princeton University
\end{itemize}

\section{Education}

\begin{itemize}[labelindent=1.5em,labelsep=2.1cm,leftmargin=2.75cm]
\setlength\itemsep{0em}
\item [\yr{2021}] Ph.D. in Public and International Affairs, Princeton University
\item[] Dissertation: \emph{Coastal Defense in an Era of Sea-Level Rise: Science, Politics, and Decision-Making} \href{https://www.dropbox.com/s/n0pa3d2w27hivd2/dmr_dissertation_1d.pdf?dl=0}{[pdf]}
\item[] Committee: \emph{Michael Oppenheimer, Robert E. Kopp, Ning Lin, Guy Nordenson}
\item [\yr{2013}] M.S. in Civil and Environmental Engineering, University of California, Davis
\item[] Thesis: \emph{The Ozone Climate Penalty: Past, Present, and Future} \href{https://www.dropbox.com/s/nba44zkt9s7yhil/MSthesis.pdf?dl=0}{[pdf]}
\item[\yr{2009}] B.S. in Atmospheric and Oceanic Science, University of Wisconsin, Madison
\item[] Thesis: \emph{An Analysis of Climate Change Impacts on Future Wind Energy Production in California} \href{https://www.dropbox.com/s/546ye739g7o3375/BSthesis.pdf?dl=0}{[pdf]}
\end{itemize}

\section{Other Professional Experience}

\begin{itemize} [labelindent=1.5em,labelsep=1cm,leftmargin=2.75cm]
\setlength\itemsep{0em}
 \item [\yr{2013--2016}] Contracted Climate Risk Analyst, Rhodium Group
\item [\yr{2014--2015}] Senior Engineer, ENVIRON/ Ramboll
\item [\yr{2012--2014}] Research Assistant and then Engineer, California Air Resources Board
\item [\yr{2010--2011}] Research Analyst, Geophysical Fluid Dynamics Laboratory/ NOAA
\item [\yr{2008--2010}] Research Assistant, UW-Madison
\end{itemize}

\section{Journal Articles}

\begin{itemize}[labelindent=1.5em,labelsep=1cm,leftmargin=1.6cm]
\setlength\itemsep{0.5em}

\item[\yr{2026}] \textbf{D.J. Rasmussen}. Multivariate bias correction of ERA5 using in-situ observations for planning and engineering. \emph{Environmental Research: Climate}. \textbf{5} (2) 025026 doi:10.1088/2752-5295/ae63ee \href{https://iopscience.iop.org/article/10.1088/2752-5295/ae63ee/pdf}{[pdf]}

\item[\yr{2025}] J. Morim,  \textbf{D.J. Rasmussen}, T. Wahl, F.M. Calafat, R.E. Kopp, and M. Oppenheimer. US-CoastEX: Observation-based probabilistic reanalysis of storm surge and sea level extremes for the United States. \emph{Scientific Data} 12, 1395. doi:10.1038/s41597-025-05730-1 \href{https://www.nature.com/articles/s41597-025-05730-1.pdf}{[pdf]}

\item[\yr{2025}] J. Morim, T. Wahl, \textbf{D.J. Rasmussen}, F.M. Calafat, S. Vitousek, S. Dangendorf, R.E. Kopp, M. Oppenheimer. Observations reveal changing coastal storms around the United States. \emph{Nature Climate Change}. doi:10.1038/s41558-025-02315-z \href{https://www.nature.com/articles/s41558-025-02315-z}{[pdf]}

\item[\yr{2023}] T.H.J. Hermans, V. Malagón-Santos, C.A. Katsman, R.A. Jane, \textbf{D.J. Rasmussen}, M. Haasnoot, G.G. Garner, R.E. Kopp, M. Oppenheimer, and A.B.A. Slangen. The Timing of Decreasing Coastal Flood Protection Due to Sea-Level Rise. \emph{Nature Climate Change}. doi:10.1038/s41558-023-01616-5 \href{https://www.nature.com/articles/s41558-023-01616-5}{[pdf]}

\item [\yr{2023}] \textbf{D.J. Rasmussen},  R.E. Kopp, and M. Oppenheimer. Coastal flood protection megaprojects in an era of sea-level rise: politically feasible strategies or Army Corps fantasies? (Editor's Choice Collection) \emph{Journal of Water Resources Planning and Management.}  \textbf{149} (2) 10.1061/(ASCE)WR.1943-5452.0001613 \href{https://ascelibrary.org/doi/10.1061/%28ASCE%29WR.1943-5452.0001613}{[pdf]}

\item [\yr{2022}] \textbf{D.J. Rasmussen}, S. Kulp, R.E. Kopp, M. Oppenheimer, and B. Strauss. Popular extreme sea level metrics can better communicate impacts (Opinion). \emph{Climatic Change.} \textbf{170} (30) doi:10.1007/s10584-021-03288-6 \href{https://link.springer.com/article/10.1007/s10584-021-03288-6}{[pdf]}

\item [\yr{2021}] B. Strauss, S. Kulp, A. Levermann, and \textbf{D.J. Rasmussen}. Unprecedented threats to cities from multi-century sea level rise. \emph{Environmental Research Letters}. \textbf{16} 114015 doi:10.1088/1748-9326/ac2e6b \href{https://iopscience.iop.org/article/10.1088/1748-9326/ac2e6b/pdf}{[pdf]}

\item [\yr{2021}] C. Tebaldi, R. Ranasinghe, M. Vousdoukas, \textbf{D.J. Rasmussen}, B. Vega-Westhoff, E. Kirezci, R.E. Kopp, R. Sriver, and L. Mentaschi. Extreme Sea Levels at Different Global Warming Levels. \emph{Nature Climate Change}. doi:10.1038/s41558-021-01127-1 \href{https://www.nature.com/articles/s41558-021-01127-1}{[pdf]}

\item [\yr{2021}] \textbf{D.J. Rasmussen}, R.E. Kopp, M. Oppenheimer, and R. Shwom. The political complexity of coastal flood risk reduction: lessons for climate adaptation public works in the U.S. \emph{Earth's Future}. \textbf{9} (2) doi:10.1029/2020EF001575 \href{https://agupubs.onlinelibrary.wiley.com/doi/abs/10.1029/2020EF001575}{[pdf]}

\item [\yr{2020}] \textbf{D.J. Rasmussen}, M.K. Buchanan, R.E. Kopp, and M. Oppenheimer. A flood damage allowance framework for coastal protection with deep uncertainty in sea-level rise. \emph{Earth's Future}. \textbf{8} (3) doi:10.1029/2019EF001340 \href{https://agupubs.onlinelibrary.wiley.com/doi/epdf/10.1029/2019EF001340}{[pdf]}

\item [\yr{2020}] T. Frederikse, M.K. Buchanan, E. Lambert, R.E. Kopp, M. Oppenheimer, \textbf{D.J. Rasmussen}, and R.S.W. van de Wal. Antarctic Ice Sheet and emission scenario controls on 21st-century extreme sea-level changes. \emph{Nature Communications}. \textbf{11} (390) doi:10.1038/s41467-019-14049-6 \href{https://www.nature.com/articles/s41467-019-14049-6.pdf}{[pdf]}

\item [\yr{2018}]  \textbf{D.J. Rasmussen}, K. Bittermann, M.K. Buchanan, S. Kulp, B.H. Strauss, R.E. Kopp, and M. Oppenheimer. Extreme sea level implications of 1.5 $^\circ$C, 2.0 $^\circ$C, and 2.5 $^\circ$C temperature stabilization targets in the 21st and 22nd century. \emph{Environmental Research Letters}. \textbf{13} 034040  doi:10.1088/1748-9326/aaac87 \href{https://iopscience.iop.org/article/10.1088/1748-9326/aaac87/pdf}{[pdf]}

\item [\yr{2017}] S.M. Hsiang, R.E. Kopp, A.S. Jina, J. Rising, M. Delgado, S. Mohan, \textbf{D.J. Rasmussen}, R. Muir-Wood, P. Wilson, M. Oppenheimer, K. Larsen, and T. Houser. Economic damage from climate change in the United States. \emph{Science}. \textbf{356} (6345), 1362-1369 doi:10.1126/science.aal4369  \href{https://www.dropbox.com/s/n8yno7jxrkuut1z/science_paper2017.pdf?dl=0}{[pdf]}

\item [\yr{2016}]  \textbf{D.J. Rasmussen}, M. Meinshausen, and R.E. Kopp. Probability-weighted ensembles of U.S. county-level climate projections for climate risk analysis. \emph{Journal of Applied Meteorology and Climatology}.  \textbf{55} (10), 2301-2322 doi:10.1175/JAMC-D-15-0302.1 \href{https://journals.ametsoc.org/doi/pdf/10.1175/JAMC-D-15-0302.1}{[pdf]}

\item [\yr{2014}]   R.E. Kopp, R. Horton, C.M. Little, J.X. Mitrovica, M. Oppenheimer, \textbf{D.J. Rasmussen}, B.H. Strauss, and C. Tebaldi. Probabilistic 21st and 22nd century sea-level rise projections at a global network of tide gauge sites. \emph{Earth's Future}. \textbf{2} (8), 383-406 doi:10.1002/2014EF000239  \href{https://www.dropbox.com/s/pebs0c3xf9adl4x/rasmussenetal_2012.pdf?dl=0}{[pdf]}

\item [\yr{2013}]  \textbf{D.J. Rasmussen}, J. Hu, A. Mahmud, and M.J. Kleeman. The ozone climate penalty: past, present, and future. \emph{Environmental Science \& Technology}. \textbf{47} (24), 14258-14266 doi:10.1021/es403446m \href{https://www.dropbox.com/s/8zu597npl927ymt/es403446m_proof.pdf?dl=0}{[pdf]}

\item [\yr{2012}]  \textbf{D.J. Rasmussen}, A.M. Fiore, V. Naik, L.W. Horowitz, M.G. Schultz, and S.J. McGinnis. Surface ozone-temperature relationships in the eastern US: A monthly climatology for evaluating chemistry-climate models. \emph{Atmospheric Environment}. \textbf{47}, 142-153 doi:10.1016/j.atmosenv.2011.11.021 \href{https://www.dropbox.com/s/pebs0c3xf9adl4x/rasmussenetal_2012.pdf?dl=0}{[pdf]}

\item [\yr{2011}]  \textbf{D.J. Rasmussen}, T. Holloway, and G.F. Nemet. Opportunities and Challenges in Assessing Climate Change Impacts on Wind Energy\textemdash A Critical Comparison of Wind Speed Projections in California. \emph{Environmental Research Letters}. \textbf{6} 024008 doi:10.1088/1748-9326/6/2/024008 \href{https://iopscience.iop.org/article/10.1088/1748-9326/6/2/024008/pdf}{[pdf]}

\end{itemize}

\section{Books}
\begin{itemize}[labelindent=1.5em,labelsep=1cm,leftmargin=1.6cm]
\item [\yr{2015}]  T. Houser, R. Kopp, S. Hsiang, R. Muir-Wood, K. Larsen, \textbf{D.J. Rasmussen}, M. Delgado, A. Jina, S. Mohan, P. Wilson, M. Mastrandrea, and J. Rising: \emph{Economic Risks of Climate Change: An American Prospectus.} New York, NY: Columbia University Press. 384 pp. ISBN: 9780231174565 \href{https://www.amazon.com/Economic-Risks-Climate-Change-Prospectus/dp/023117456X}{[link]}
\end{itemize}


\section{Software \& Data Products}
\begin{itemize}[labelindent=1.5em,labelsep=1cm,leftmargin=1.6cm]
\setlength\itemsep{0.5em}
\item[\yr{2026}] \textbf{D.J. Rasmussen}. \emph{SCOPE-ERA5: Station-Calibrated Outputs for Planning \& Engineering---ERA5} [Data set]. Zenodo. doi:10.5281/zenodo.15611601 \href{https://doi.org/10.5281/zenodo.15611601}{[link]}
\end{itemize}


\section{Research Reports}

\begin{itemize}[labelindent=1.5em,labelsep=1cm,leftmargin=1.6cm]
\setlength\itemsep{0em}

\item[\yr{2015}] U. Nopmongcol, J. Johnson, B. Brashers, \textbf{D.J. Rasmussen}, T. Shah, J. Zagunis, Z. Liu, and R. Morris: \emph{Formation of Secondary PM$_{2.5}$ in the Capital Region Study.} Prepared for Environmental and Sustainable Resource Development, Edmonton, AB. \href{https://www.dropbox.com/s/6wwnkeby8yndri9/2015-FormationSecPM2.5CapitalReg-Report-2015.pdf?dl=0}{[pdf]}

\item [\yr{2015}] C. Emery, G. Wilson, \textbf{D.J. Rasmussen}, G. Yarwood: \emph{CAMx Speed Improvements.} Prepared for Texas Commission on Environmental Quality, Austin, TX. \href{5821550417FY1535-20150731-environ-camx_speed_improvement.pdf}{[pdf]}

\item [\yr{2015}] J. Johnson, G. Wilson, \textbf{D.J. Rasmussen}, G. Yarwood: \emph{Daily Near Real-Time Ozone Modeling for Texas.} Prepared for Texas Commission on Environmental Quality, Austin, TX. \href{https://www.dropbox.com/s/9ju5z2ow9c7lpko/5821110365FY1416-20150129-environ-NRT_O3_modeling_phase2.pdf?dl=0}{[pdf]}

\item [\yr{2014}] S. Kemball-Cook, T. Pavlovic, J. Johnson, L. Parker, \textbf{D.J. Rasmussen}, J. Zagunis, L. Ma, G. Yarwood: \emph{Analysis of Wildfire Impacts on High Ozone Days in Houston, Beaumont, and Dallas-Fort Worth During 2012 and 2013.} Prepared for Texas Commission on Environmental Quality, Austin, TX. \href{https://www.dropbox.com/s/kfeb4wm98wiuyca/5821110365FY1419-20140731-environ-wildfire_ozone_impact.pdf?dl=0} {[pdf]}

\item [\yr{2014}]  T. Houser, R. Kopp, S. Hsiang, R. Muir-Wood, K. Larsen, \textbf{D.J. Rasmussen}, M. Delgado, A. Jina, S. Mohan, P. Wilson, M. Mastrandrea, and J. Rising: \emph{American Climate Prospectus: Economic Risks in the United States.} Oakland, CA: Rhodium Group, 194 pp. \href{https://www.dropbox.com/s/whigxyzshopcgmz/AmericanClimateProspectus_v1.2.pdf?dl=0}{[pdf]}

\item [\yr{2012}] \textbf{D.J. Rasmussen} and M.J. Kleeman: Acceleration of CALPUFF using MPICH-2. Final Report to the California Air Resources Board. ARB Contract 11-760. \href{https://www.dropbox.com/s/dti8dfaohikwkth/parallel_CALPUFF_FINALreport_CARB.pdf?dl=0}{[pdf]}

\item [\yr{2010}] \textbf{D.J. Rasmussen}, L.M. Keller, and M.A. Lazzara: A 20-year assessment of the frequency and intensity of McMurdo area high wind events. Preprints, \emph{5$^{th}$ Antarctic Meteorological Observation, Modeling, and Forecasting Workshop} \href{https://www.dropbox.com/s/zmtpe7ld9i177am/bprc_technical_report_2010-01.pdf?dl=0}{[pdf]}

\end{itemize}


\section{Presentations}

\begin{itemize}[labelindent=1.5em,labelsep=1cm,leftmargin=1.6cm]
\setlength\itemsep{0em}
\item[\yr{2026}] ASHRAE Annual Conference, Austin, TX. ``Global 1-km Climatic Design Extremes at Ungauged Locations via Machine Learning Regionalization of Extreme Value Parameters,'' Paper Session 20: Advanced Heat Pumps, Ventilation, and Climate Data (\emph{Poster}, AU-26-C074)
\item[\yr{2023}] American Geophysical Union Fall Meeting, San Francisco, CA. ``Storm surge reanalysis of Hurricane Idalia using a spatial Bayesian model'' (NH21D-06)
\item[\yr{2023}] American Geophysical Union Fall Meeting, San Francisco, CA. ``Applying Allowances: A non-stationary, risk-based approach for advancing facility design to sea level rise and other climate hazards'' (NH44A-02)
\item[\yr{2021}] NASA Goddard Institute for Space Studies (\emph{Invited})
\item[\yr{2021}] Woodwell Climate Research Center, Virtual (\emph{Invited})
\item[\yr{2021}] American Geophysical Union Natural Hazards Meeting, Virtual (\emph{Invited})
\item[\yr{2021}] Association of State Floodplain Managers Conference, Virtual
\item[\yr{2021}] UC-Irvine Departmental Seminar, Virtual (\emph{Invited})
\item[\yr{2021}] Coastal State Discussion Series (Rhode Island): The Future of Coastal Megaprojects, Virtual (\emph{Invited}) \href{https://www.youtube.com/watch?v=PGbNXaviStM}{[video]}
\item[\yr{2020}] American Geophysical Union Fall Meeting, Virtual
\item[\yr{2017}] American Geophysical Union Fall Meeting, New Orleans, LA
\item[\yr{2015}] American Geophysical Union Fall Meeting,  San Francisco, CA  \href{https://www.dropbox.com/s/t4tsj83gemdp09a/rasmussen_AGU2015_v2_flat.pdf?dl=0}{[poster]}
\item[\yr{2014}] American Geophysical Union Fall Meeting,  San Francisco, CA \href{https://www.dropbox.com/s/t0rufelj5atpuk4/2014-12%20ACP%20wetbulb%20talk%20AGU.pdf?dl=0}{[slides]}
\item[\yr{2011}] American Geophysical Union Fall Meeting,  San Francisco, CA  \href{https://www.dropbox.com/s/s511oapbyqasclh/AGU_ozone_temp_120511_final.pptx?dl=0}{[slides]}
\end{itemize}

\section{Public Outreach}

\begin{itemize}[labelindent=1.5em,labelsep=1cm,leftmargin=1.6cm]
\setlength\itemsep{0em}
 \item[\yr{2021}] The largest movable structures on Earth could save New York City from another Hurricane Sandy, but will they get built?, \emph{Princeton Research Day} \href{https://mediacentral.princeton.edu/media/The+largest+movable+structures+on+Earth+could+save+New+York+City+from+another+Hurricane+Sandy%2C+but+will+they+get+builtF%2C+D.J.+Rasmussen+%282309867%29/1_qernsj6u}{[Link]}
 \item[\yr{2020}] What can climate adaptation learn from what's in Grandpa's garage? A historical tale of two flood protection megastructures, \emph{Highwire Earth} \href{https://highwire.princeton.edu/2020/12/18/what-can-climate-adaptation-learn-from-whats-in-grandpas-garage-a-historical-tale-of-two-flood-protection-megastructures/}{[Link]}
 \item[\yr{2020}] \emph{Could megastructures save New York City from another Hurricane Sandy?}, short film (independently produced) \href{https://www.youtube.com/watch?v=UAyN-i6AYY8&t=5s}{[Link]}
 \item[\yr{2020}] Eight years after Hurricane Sandy New Yorkers are still waiting for flood protection, \emph{C-PREE Blog} \href{https://cpree.princeton.edu/news/opinion-video-eight-years-after-hurricane-sandy-new-yorkers-are-still-waiting-flood-protection}{[Link]}
\end{itemize}

\section{Awards and Grants}
\begin{itemize}[labelindent=1.5em,labelsep=1cm,leftmargin=1.6cm]
\setlength\itemsep{0em}
 \item[\yr{2020--2021}] Dissertation Completion Fellowship/Post-graduate Research Associate (Princeton)
 \item[\yr{2019}] Karl F. Schlaepfer '49 and Gloria G. Schlaepfer Fund (Princeton)
\end{itemize}



\section{Professional Service}
\begin{itemize}[labelindent=1.5em,leftmargin=0cm]
\item[] American Society of Civil Engineers, Committee on Adaptation to a Changing Climate (2025--)
\item[] U.S. Green Buildings Council, LEED v5 Resilience Working Group (2023--2024)
\item[] Invited panelist for ``Water, Water Everywhere: Climate Change, Flooding and the Gowanus Rezone'', Hosted by: \emph{Voice of Gowanus}, 2021  \href{https://citylimits.org/2021/05/13/gowanus-rezoning-critics-highlight-impact-of-climate-on-future-flooding-as-public-review-moves-forward/}{[Link]}
 \item[] Informal Reviewer, IPCC Special Report on the Ocean and Cryosphere in a Changing Climate, 2019
 \item[] American Meteorological Society, Energy Committee (2011--2013)
 \item[] Reviewer: \emph{Nature Clim. Change, J. Geophys. Res.-Oceans, Environ. Res. Lett., Earth's Future, Clim. Chang., Sci. Rep., Atmos. Chem. Phys., Atmos. Environ., J. Flood Risk Manag., Atmos. Res., J. Waterw. Port Coast. Ocean Eng., Environ. Res. Comm., Ocean Coast. Manag., Commun. Earth Environ.}
\end{itemize}

\section{Teaching}
TA, \emph{The Environment: Science and Policy} (Princeton University, Spring 2017, 2018)

\section{Hobbies}
 Alpine skiing, CrossFit, AcroYoga, guitar, photography and film

\section{Citizenship}
 USA

\bigskip
\begin{center}
  \begin{footnotesize}\sffamily
    Last updated: \today
  \end{footnotesize}
\end{center}

\end{document}
