%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Curriculum Vitae — D.J. Rasmussen, Ph.D.
%% Modern single-column layout (monochrome, ATS/OCR-safe), dmr 2026
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10.5pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[T1]{fontenc}
\usepackage{newpxtext}                 % Palatino-like serif body
\usepackage[scaled=0.90]{helvet}       % sans for name, headers, year column
\usepackage[tracking=true]{microtype}  % kerning + letterspacing for headers

\usepackage{calc}
\usepackage{enumitem}
\usepackage{graphicx}

% Full-width single column — reclaims the page from the old margin-note titles
\usepackage[letterpaper,
            left=0.8in, right=0.8in,
            top=0.7in,  bottom=0.85in]{geometry}

\setlength{\parindent}{0pt}

\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\definecolor{rulegray}{gray}{0.55}
\hypersetup{breaklinks,colorlinks,
            linkcolor=darkblue, urlcolor=darkblue,
            anchorcolor=darkblue, citecolor=darkblue}

%%% Running header / footer
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\rhead{\footnotesize\sffamily\color{rulegray} D.\,J.~Rasmussen \textperiodcentered\ p.~\arabic{page} of \pageref*{LastPage}}
\fancypagestyle{plain}{\fancyhf{}\renewcommand{\headrulewidth}{0pt}%
  \rhead{\footnotesize\sffamily\color{rulegray} D.\,J.~Rasmussen \textperiodcentered\ p.~\arabic{page} of \pageref*{LastPage}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Section header: letterspaced bold sans caps over a full-width hairline rule.
\newcommand{\cvsection}[1]{%
  \par\addvspace{12pt}\pagebreak[3]%
  {\sffamily\bfseries\small\textls[80]{\MakeUppercase{#1}}}%
  \par\vspace{2pt}%
  {\color{rulegray}\hrule height 0.6pt}%
  \vspace{5pt}\nopagebreak}
\renewcommand{\section}[1]{\cvsection{#1}}

% Year label in the left column (bold sans).
\newcommand{\yr}[1]{{\sffamily\bfseries #1}}

% Dated-entry list: fixed year column on the left, body hangs aligned.
% Used consistently across every dated section.
\newlist{entries}{description}{1}
\setlist[entries]{
  style=sameline, align=left, font=\normalfont,
  leftmargin=1.85cm, labelwidth=1.55cm, labelsep=0.3cm,
  labelindent=0pt, itemindent=0pt,
  itemsep=0.42\baselineskip, parsep=0pt, topsep=1pt, partopsep=0pt}

% Compact bulleted list for undated items (e.g. Professional Service).
\newlist{cvbullets}{itemize}{1}
\setlist[cvbullets]{
  leftmargin=1.4em, label=\textbullet,
  itemsep=0.35\baselineskip, parsep=0pt, topsep=1pt, partopsep=0pt}

\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}
\providecommand*\email[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%% Masthead: name + inline contact line, over a rule
\begin{center}
  {\LARGE\sffamily\bfseries\textls[50]{D.\,J.~Rasmussen, Ph.D.}}\\[5pt]
  {\small\sffamily
   \email{dj.rasmussen@degreeday.org}\enspace\textbullet\enspace
   \href{https://www.djrasmussen.co/}{www.djrasmussen.co}\enspace\textbullet\enspace
   \href{http://scholar.google.com/citations?user=yocPWzYAAAAJ&hl=en}{Google Scholar}\enspace\textbullet\enspace
   ORCID~\href{https://orcid.org/0000-0003-4668-5749}{0000-0003-4668-5749}}
\end{center}
\vspace{3pt}
\hrule height 1pt
\vspace{-2pt}

\section{Recent Professional Experience}
\begin{entries}
\item[\yr{2025--now}] Founder and Principal, \href{https://www.degreeday.org/}{Degree Day}
\item[\yr{2022--2025}] Lead Consultant, later Associate Vice President (AVP), \href{https://www.wsp.com/}{WSP} (Sept.~2022--Jan.~2025)
\item[\yr{2022}] Risk and Resilience Engineer, \href{https://www.arup.com/}{Arup} (Jan.--Aug.~2022)
\item[\yr{2021--2022}] Postdoctoral Research Associate, \href{https://spia.princeton.edu/}{School of Public and International Affairs}, Princeton University
\end{entries}

\section{Education}
\begin{entries}
\item[\yr{2021}] Ph.D. in Public and International Affairs, Princeton University
\item[] Dissertation: \emph{Coastal Defense in an Era of Sea-Level Rise: Science, Politics, and Decision-Making} \href{https://www.dropbox.com/s/n0pa3d2w27hivd2/dmr_dissertation_1d.pdf?dl=0}{[pdf]}
\item[] Committee: \emph{Michael Oppenheimer, Robert E. Kopp, Ning Lin, Guy Nordenson}
\item[\yr{2013}] M.S. in Civil and Environmental Engineering, University of California, Davis
\item[] Thesis: \emph{The Ozone Climate Penalty: Past, Present, and Future} \href{https://djrasmussen.co/assets/papers/MSthesis.pdf}{[pdf]}
\item[\yr{2009}] B.S. in Atmospheric and Oceanic Science, University of Wisconsin, Madison
\item[] Thesis: \emph{An Analysis of Climate Change Impacts on Future Wind Energy Production in California} \href{https://djrasmussen.co/assets/papers/BSthesis.pdf}{[pdf]}
\end{entries}

\section{Other Professional Experience}
\begin{entries}
\item[\yr{2013--2016}] Contracted Climate Risk Analyst, \href{https://rhg.com/}{Rhodium Group}
\item[\yr{2014--2015}] Senior Engineer, \href{https://www.ramboll.com/}{ENVIRON/ Ramboll}
\item[\yr{2012--2014}] Research Assistant and then Engineer, \href{https://ww2.arb.ca.gov/}{California Air Resources Board}
\item[\yr{2010--2011}] Research Analyst, \href{https://www.gfdl.noaa.gov/}{Geophysical Fluid Dynamics Laboratory}/ NOAA
\item[\yr{2008--2010}] Research Assistant, \href{https://www.wisc.edu/}{UW-Madison}
\end{entries}

\section{Journal Articles}
\begin{entries}
\item[\yr{2026}] \textbf{D.J. Rasmussen}. Multivariate bias correction of ERA5 using in-situ observations for planning and engineering. \emph{Environmental Research: Climate}. \textbf{5} (2) 025026 doi:10.1088/2752-5295/ae63ee \href{https://iopscience.iop.org/article/10.1088/2752-5295/ae63ee/pdf}{[pdf]}
\item[\yr{2025}] J. Morim, \textbf{D.J. Rasmussen}, T. Wahl, F.M. Calafat, R.E. Kopp, and M. Oppenheimer. US-CoastEX: Observation-based probabilistic reanalysis of storm surge and sea level extremes for the United States. \emph{Scientific Data} 12, 1395. doi:10.1038/s41597-025-05730-1 \href{https://www.nature.com/articles/s41597-025-05730-1.pdf}{[pdf]}
\item[\yr{2025}] J. Morim, T. Wahl, \textbf{D.J. Rasmussen}, F.M. Calafat, S. Vitousek, S. Dangendorf, R.E. Kopp, M. Oppenheimer. Observations reveal changing coastal storms around the United States. \emph{Nature Climate Change}. doi:10.1038/s41558-025-02315-z \href{https://www.nature.com/articles/s41558-025-02315-z}{[pdf]}
\item[\yr{2023}] T.H.J. Hermans, V. Malagón-Santos, C.A. Katsman, R.A. Jane, \textbf{D.J. Rasmussen}, M. Haasnoot, G.G. Garner, R.E. Kopp, M. Oppenheimer, and A.B.A. Slangen. The Timing of Decreasing Coastal Flood Protection Due to Sea-Level Rise. \emph{Nature Climate Change}. doi:10.1038/s41558-023-01616-5 \href{https://www.nature.com/articles/s41558-023-01616-5}{[pdf]}
\item[\yr{2023}] \textbf{D.J. Rasmussen}, R.E. Kopp, and M. Oppenheimer. Coastal flood protection megaprojects in an era of sea-level rise: politically feasible strategies or Army Corps fantasies? (Editor's Choice Collection) \emph{Journal of Water Resources Planning and Management.} \textbf{149} (2) 10.1061/(ASCE)WR.1943-5452.0001613 \href{https://ascelibrary.org/doi/10.1061/%28ASCE%29WR.1943-5452.0001613}{[pdf]}
\item[\yr{2022}] \textbf{D.J. Rasmussen}, S. Kulp, R.E. Kopp, M. Oppenheimer, and B. Strauss. Popular extreme sea level metrics can better communicate impacts (Opinion). \emph{Climatic Change.} \textbf{170} (30) doi:10.1007/s10584-021-03288-6 \href{https://link.springer.com/article/10.1007/s10584-021-03288-6}{[pdf]}
\item[\yr{2021}] B. Strauss, S. Kulp, A. Levermann, and \textbf{D.J. Rasmussen}. Unprecedented threats to cities from multi-century sea level rise. \emph{Environmental Research Letters}. \textbf{16} 114015 doi:10.1088/1748-9326/ac2e6b \href{https://iopscience.iop.org/article/10.1088/1748-9326/ac2e6b/pdf}{[pdf]}
\item[\yr{2021}] C. Tebaldi, R. Ranasinghe, M. Vousdoukas, \textbf{D.J. Rasmussen}, B. Vega-Westhoff, E. Kirezci, R.E. Kopp, R. Sriver, and L. Mentaschi. Extreme Sea Levels at Different Global Warming Levels. \emph{Nature Climate Change}. doi:10.1038/s41558-021-01127-1 \href{https://www.nature.com/articles/s41558-021-01127-1}{[pdf]}
\item[\yr{2021}] \textbf{D.J. Rasmussen}, R.E. Kopp, M. Oppenheimer, and R. Shwom. The political complexity of coastal flood risk reduction: lessons for climate adaptation public works in the U.S. \emph{Earth's Future}. \textbf{9} (2) doi:10.1029/2020EF001575 \href{https://agupubs.onlinelibrary.wiley.com/doi/abs/10.1029/2020EF001575}{[pdf]}
\item[\yr{2020}] \textbf{D.J. Rasmussen}, M.K. Buchanan, R.E. Kopp, and M. Oppenheimer. A flood damage allowance framework for coastal protection with deep uncertainty in sea-level rise. \emph{Earth's Future}. \textbf{8} (3) doi:10.1029/2019EF001340 \href{https://agupubs.onlinelibrary.wiley.com/doi/epdf/10.1029/2019EF001340}{[pdf]}
\item[\yr{2020}] T. Frederikse, M.K. Buchanan, E. Lambert, R.E. Kopp, M. Oppenheimer, \textbf{D.J. Rasmussen}, and R.S.W. van de Wal. Antarctic Ice Sheet and emission scenario controls on 21st-century extreme sea-level changes. \emph{Nature Communications}. \textbf{11} (390) doi:10.1038/s41467-019-14049-6 \href{https://www.nature.com/articles/s41467-019-14049-6.pdf}{[pdf]}
\item[\yr{2018}] \textbf{D.J. Rasmussen}, K. Bittermann, M.K. Buchanan, S. Kulp, B.H. Strauss, R.E. Kopp, and M. Oppenheimer. Extreme sea level implications of 1.5 $^\circ$C, 2.0 $^\circ$C, and 2.5 $^\circ$C temperature stabilization targets in the 21st and 22nd century. \emph{Environmental Research Letters}. \textbf{13} 034040 doi:10.1088/1748-9326/aaac87 \href{https://iopscience.iop.org/article/10.1088/1748-9326/aaac87/pdf}{[pdf]}
\item[\yr{2017}] S.M. Hsiang, R.E. Kopp, A.S. Jina, J. Rising, M. Delgado, S. Mohan, \textbf{D.J. Rasmussen}, R. Muir-Wood, P. Wilson, M. Oppenheimer, K. Larsen, and T. Houser. Economic damage from climate change in the United States. \emph{Science}. \textbf{356} (6345), 1362-1369 doi:10.1126/science.aal4369 \href{https://doi.org/10.1126/science.aal4369}{[link]}
\item[\yr{2016}] \textbf{D.J. Rasmussen}, M. Meinshausen, and R.E. Kopp. Probability-weighted ensembles of U.S. county-level climate projections for climate risk analysis. \emph{Journal of Applied Meteorology and Climatology}. \textbf{55} (10), 2301-2322 doi:10.1175/JAMC-D-15-0302.1 \href{https://journals.ametsoc.org/doi/pdf/10.1175/JAMC-D-15-0302.1}{[pdf]}
\item[\yr{2014}] R.E. Kopp, R. Horton, C.M. Little, J.X. Mitrovica, M. Oppenheimer, \textbf{D.J. Rasmussen}, B.H. Strauss, and C. Tebaldi. Probabilistic 21st and 22nd century sea-level rise projections at a global network of tide gauge sites. \emph{Earth's Future}. \textbf{2} (8), 383-406 doi:10.1002/2014EF000239 \href{https://agupubs.onlinelibrary.wiley.com/doi/epdf/10.1002/2014EF000239}{[pdf]}
\item[\yr{2013}] \textbf{D.J. Rasmussen}, J. Hu, A. Mahmud, and M.J. Kleeman. The ozone climate penalty: past, present, and future. \emph{Environmental Science \& Technology}. \textbf{47} (24), 14258-14266 doi:10.1021/es403446m \href{https://doi.org/10.1021/es403446m}{[link]}
\item[\yr{2012}] \textbf{D.J. Rasmussen}, A.M. Fiore, V. Naik, L.W. Horowitz, M.G. Schultz, and S.J. McGinnis. Surface ozone-temperature relationships in the eastern US: A monthly climatology for evaluating chemistry-climate models. \emph{Atmospheric Environment}. \textbf{47}, 142-153 doi:10.1016/j.atmosenv.2011.11.021 \href{https://doi.org/10.1016/j.atmosenv.2011.11.021}{[link]}
\item[\yr{2011}] \textbf{D.J. Rasmussen}, T. Holloway, and G.F. Nemet. Opportunities and Challenges in Assessing Climate Change Impacts on Wind Energy\textemdash A Critical Comparison of Wind Speed Projections in California. \emph{Environmental Research Letters}. \textbf{6} 024008 doi:10.1088/1748-9326/6/2/024008 \href{https://iopscience.iop.org/article/10.1088/1748-9326/6/2/024008/pdf}{[pdf]}
\end{entries}

\section{Books}
\begin{entries}
\item[\yr{2015}] T. Houser, R. Kopp, S. Hsiang, R. Muir-Wood, K. Larsen, \textbf{D.J. Rasmussen}, M. Delgado, A. Jina, S. Mohan, P. Wilson, M. Mastrandrea, and J. Rising: \emph{Economic Risks of Climate Change: An American Prospectus.} New York, NY: Columbia University Press. 384 pp. ISBN: 9780231174565 \href{https://www.amazon.com/Economic-Risks-Climate-Change-Prospectus/dp/023117456X}{[link]}
\end{entries}

\section{Software \& Data Products}
\begin{entries}
\item[\yr{2026}] \textbf{D.J. Rasmussen}. \emph{SCOPE-ERA5: Station-Calibrated Outputs for Planning \& Engineering---ERA5} [Data set]. Zenodo. doi:10.5281/zenodo.15611601 \href{https://doi.org/10.5281/zenodo.15611601}{[link]}
\item[\yr{2026}] \textbf{D.J. Rasmussen}. \emph{SCOPE-CMIP6: Station Climate-Indicator Distributions by Global Warming Level} (v0.1) [Data set]. Zenodo. doi:10.5281/zenodo.21361665 \href{https://doi.org/10.5281/zenodo.21361665}{[link]}
\item[\yr{2026}] \textbf{D.J. Rasmussen}. \emph{SCOPE-CORDEX: Station Climate-Indicator Distributions by Global Warming Level} (v0.1) [Data set]. Zenodo. doi:10.5281/zenodo.21361663 \href{https://doi.org/10.5281/zenodo.21361663}{[link]}
\item[\yr{2026}] \textbf{D.J. Rasmussen}. \emph{CAHDC: Climate-Adjusted HVAC Design Conditions} (v0.1) [Data set]. Zenodo. doi:10.5281/zenodo.21330963 \href{https://doi.org/10.5281/zenodo.21330963}{[link]}
\item[\yr{2026}] \textbf{D.J. Rasmussen}. \emph{GloIDF: A Global Present-Climate Sub-Daily Rainfall Intensity--Duration--Frequency (IDF) Dataset at 30 Arc-Second Resolution} (v0.1) [Data set]. Zenodo. doi:10.5281/zenodo.21331633 \href{https://doi.org/10.5281/zenodo.21331633}{[link]}
\item[\yr{2017}] \textbf{D.J. Rasmussen} and R.E. Kopp. \emph{Probability-Weighted Ensembles of U.S. County-Level Climate Projections for Climate Impact Modeling} [Data set]. Zenodo. doi:10.5281/zenodo.582327 \href{https://doi.org/10.5281/zenodo.582327}{[link]}
\end{entries}

\section{Research Reports}
\begin{entries}
\item[\yr{2015}] U. Nopmongcol, J. Johnson, B. Brashers, \textbf{D.J. Rasmussen}, T. Shah, J. Zagunis, Z. Liu, and R. Morris: \emph{Formation of Secondary PM$_{2.5}$ in the Capital Region Study.} Prepared for Environmental and Sustainable Resource Development, Edmonton, AB. \href{https://open.alberta.ca/dataset/bba204ba-c516-4a96-9025-0420fc18f401/resource/e111dd78-8c2f-400b-b048-de152a279f8d/download/2015-FormationSecPM2.5CapitalReg-Report-2015.pdf}{[pdf]}
\item[\yr{2015}] C. Emery, G. Wilson, \textbf{D.J. Rasmussen}, G. Yarwood: \emph{CAMx Speed Improvements.} Prepared for Texas Commission on Environmental Quality, Austin, TX. \href{https://wayback.archive-it.org/414/20210529064701/https://www.tceq.texas.gov/assets/public/implementation/air/am/contracts/reports/pm/5821550417FY1535-20150731-environ-camx_speed_improvement.pdf}{[pdf]}
\item[\yr{2015}] J. Johnson, G. Wilson, \textbf{D.J. Rasmussen}, G. Yarwood: \emph{Daily Near Real-Time Ozone Modeling for Texas.} Prepared for Texas Commission on Environmental Quality, Austin, TX.
\item[\yr{2014}] S. Kemball-Cook, T. Pavlovic, J. Johnson, L. Parker, \textbf{D.J. Rasmussen}, J. Zagunis, L. Ma, G. Yarwood: \emph{Analysis of Wildfire Impacts on High Ozone Days in Houston, Beaumont, and Dallas-Fort Worth During 2012 and 2013.} Prepared for Texas Commission on Environmental Quality, Austin, TX.
\item[\yr{2014}] T. Houser, R. Kopp, S. Hsiang, R. Muir-Wood, K. Larsen, \textbf{D.J. Rasmussen}, M. Delgado, A. Jina, S. Mohan, P. Wilson, M. Mastrandrea, and J. Rising: \emph{American Climate Prospectus: Economic Risks in the United States.} Oakland, CA: Rhodium Group, 194 pp. \href{https://impactlab.org/wp-content/uploads/2017/10/AmericanClimateProspectus_v1.2.pdf}{[pdf]}
\item[\yr{2012}] \textbf{D.J. Rasmussen} and M.J. Kleeman: Acceleration of CALPUFF using MPICH-2. Final Report to the California Air Resources Board. ARB Contract 11-760. \href{https://djrasmussen.co/assets/papers/parallel_CALPUFF_FINALreport_CARB.pdf}{[pdf]}
\item[\yr{2010}] \textbf{D.J. Rasmussen}, L.M. Keller, and M.A. Lazzara: A 20-year assessment of the frequency and intensity of McMurdo area high wind events. Preprints, \emph{5$^{th}$ Antarctic Meteorological Observation, Modeling, and Forecasting Workshop}
\end{entries}

\section{Presentations}
\begin{entries}
\item[\yr{2026}] ASHRAE Annual Conference, Austin, TX. ``Global 1-km Climatic Design Extremes at Ungauged Locations via Machine Learning Regionalization of Extreme Value Parameters,'' Paper Session 20: Advanced Heat Pumps, Ventilation, and Climate Data (\emph{Poster}, AU-26-C074)
\item[\yr{2023}] American Geophysical Union Fall Meeting, San Francisco, CA. ``Storm surge reanalysis of Hurricane Idalia using a spatial Bayesian model'' (NH21D-06)
\item[\yr{2023}] American Geophysical Union Fall Meeting, San Francisco, CA. ``Applying Allowances: A non-stationary, risk-based approach for advancing facility design to sea level rise and other climate hazards'' (NH44A-02)
\item[\yr{2021}] NASA Goddard Institute for Space Studies (\emph{Invited})
\item[\yr{2021}] Woodwell Climate Research Center, Virtual (\emph{Invited})
\item[\yr{2021}] American Geophysical Union Natural Hazards Meeting, Virtual (\emph{Invited})
\item[\yr{2021}] Association of State Floodplain Managers Conference, Virtual
\item[\yr{2021}] UC-Irvine Departmental Seminar, Virtual (\emph{Invited})
\item[\yr{2021}] Coastal State Discussion Series (Rhode Island): The Future of Coastal Megaprojects, Virtual (\emph{Invited}) \href{https://www.youtube.com/watch?v=PGbNXaviStM}{[video]}
\item[\yr{2020}] American Geophysical Union Fall Meeting, Virtual
\item[\yr{2017}] American Geophysical Union Fall Meeting, New Orleans, LA
\item[\yr{2015}] American Geophysical Union Fall Meeting, San Francisco, CA
\item[\yr{2014}] American Geophysical Union Fall Meeting, San Francisco, CA
\item[\yr{2011}] American Geophysical Union Fall Meeting, San Francisco, CA
\end{entries}

\section{Public Outreach}
\begin{entries}
\item[\yr{2021}] The largest movable structures on Earth could save New York City from another Hurricane Sandy, but will they get built?, \emph{Princeton Research Day} \href{https://mediacentral.princeton.edu/media/The+largest+movable+structures+on+Earth+could+save+New+York+City+from+another+Hurricane+Sandy%2C+but+will+they+get+builtF%2C+D.J.+Rasmussen+%282309867%29/1_qernsj6u}{[Link]}
\item[\yr{2020}] What can climate adaptation learn from what's in Grandpa's garage? A historical tale of two flood protection megastructures, \emph{Highwire Earth} \href{https://highwire.princeton.edu/2020/12/18/what-can-climate-adaptation-learn-from-whats-in-grandpas-garage-a-historical-tale-of-two-flood-protection-megastructures/}{[Link]}
\item[\yr{2020}] \emph{Could megastructures save New York City from another Hurricane Sandy?}, short film (independently produced) \href{https://www.youtube.com/watch?v=UAyN-i6AYY8&t=5s}{[Link]}
\item[\yr{2020}] Eight years after Hurricane Sandy New Yorkers are still waiting for flood protection, \emph{C-PREE Blog} \href{https://cpree.princeton.edu/news/opinion-video-eight-years-after-hurricane-sandy-new-yorkers-are-still-waiting-flood-protection}{[Link]}
\end{entries}

\section{Awards and Grants}
\begin{entries}
\item[\yr{2020--2021}] Dissertation Completion Fellowship/Post-graduate Research Associate (Princeton)
\item[\yr{2019}] Karl F. Schlaepfer '49 and Gloria G. Schlaepfer Fund (Princeton)
\end{entries}

\section{Professional Service}
\begin{cvbullets}
\item American Society of Civil Engineers, Committee on Adaptation to a Changing Climate (2025--)
\item U.S. Green Buildings Council, LEED v5 Resilience Working Group (2023--2024)
\item Invited panelist for ``Water, Water Everywhere: Climate Change, Flooding and the Gowanus Rezone'', Hosted by: \emph{Voice of Gowanus}, 2021 \href{https://citylimits.org/2021/05/13/gowanus-rezoning-critics-highlight-impact-of-climate-on-future-flooding-as-public-review-moves-forward/}{[Link]}
\item Informal Reviewer, IPCC Special Report on the Ocean and Cryosphere in a Changing Climate, 2019
\item American Meteorological Society, Energy Committee (2011--2013)
\item Reviewer: \emph{Nature Climate Change, Journal of Geophysical Research: Oceans, Environmental Research Letters, Earth's Future, Climatic Change, Scientific Reports, Atmospheric Chemistry and Physics, Atmospheric Environment, Journal of Flood Risk Management, Atmospheric Research, Journal of Waterway, Port, Coastal, and Ocean Engineering, Environmental Research Communications, Ocean \& Coastal Management, Communications Earth \& Environment}
\end{cvbullets}

\section{Teaching}
TA, \emph{The Environment: Science and Policy} (Princeton University, Spring 2017, 2018)

\section{Additional Information}
\textbf{Hobbies:} Alpine skiing, CrossFit, AcroYoga, guitar, photography and film \\
\textbf{Citizenship:} USA

\vspace{1.2\baselineskip}
\begin{center}
  {\footnotesize\sffamily\color{rulegray} Last updated: \today}
\end{center}

\end{document}
